RNeXML: a package for reading and writing richly annotated phylogenetic, character, and trait data in R

### 2014-08-21 manuscripts/manuscript.Rmd
added parens after link to render properly

From the list of namespaces in `prefixes`, we can follow links a handful
of established vocabularies and find terms that are not included in
`add_basic_meta()`.  For instance, by resolving the location identified
by the `prism` prefix,

@@

The `RNeXML` package is available through the CRAN repository under
a CC0 license. At the time of writing, the current version is `r packageDescription("RNeXML", fields="Version")`. 
The current development
branch can be found on Github at [https://github.com/ropensci/RNeXML].
See the NEWS file for changes in recent versions. Users are encouraged
to submit bug reports or feature requests in the issues log.  Contact
`ropensci-discuss@googlegroups.com` or the package maintainer for help,
or email the phylogenetics R users group list at `r-sig-phylo@r-project.org`.

>>>>

From the list of namespaces in `prefixes`, we can follow links to a handful
of established vocabularies and find terms that are not included in
`add_basic_meta()`.  For instance, by resolving the location identified
by the `prism` prefix,

@@

The `RNeXML` package is available through the CRAN repository under
a CC0 license. At the time of writing, the current version is `r packageDescription("RNeXML", fields="Version")`. 
The current development
branch can be found on Github at [https://github.com/ropensci/RNeXML]().
See the NEWS file for changes in recent versions. Users are encouraged
to submit bug reports or feature requests in the issues log.  Contact
`ropensci-discuss@googlegroups.com` or the package maintainer for help,
or email the phylogenetics R users group list at `r-sig-phylo@r-project.org`.
